Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-06 sections/observations.tex
Added a bit mor edetail to the smoothing section, and added a reference for savitzky-golay
Added better specs for radio data in Observations.

Minimal cloud cover and no sustained winds on the day of the eclipse contributed to a nearly issue free radio lightcurve.
We addressed 3 sources of error in our project: A strong gust of wind pushed the telescope off target for a few seconds, an issue with the accuracy of our polar alignment, causing the telescope to be slightly off target by the end of observation, and local sources of interference.

@@

Normalization is the process by which the data of a graph is scaled by a constant such that the highest points are equal to 100, essentially making the data a percentage of its highest value.

>>>>

Radio Observations took place on April 8th, 2024 at the University of Central Arkansas campus in Conway, Arkansas at approximately 35°04'51"N 92°27'36"W with an elevation of 94 m.
We began collecting data at 2460409.2186657293 JD and ended at 2460409.3424835186 JD, or 2024-04-08 17:14:53 UTC and 2024-04-08 20:13:11 UTC.
The telescope used was a Spider 230C radio telescope, a 2.3 m parabolic dish tuned to the electron spin-flip transition of Hydrogen at 1420 MHz.
During observation, we encountered minimal cloud cover and no sustained winds.
Despite this, we did have 3 sources of error: A strong gust of wind pushed the telescope off target for a few seconds, an issue with the accuracy of our polar alignment caused the telescope to be slightly off target by the end of observation, and local sources of interference created noise in the data.

@@
